---
title: "Madhav Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter","facebook","menu"]
    source_code: embed
    
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)


```


```{r}

data<-read.csv("Car Data.csv")

```

```{r}
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```


Interactive Data Visualization
==================================================

Row
------------------------------------

### Car Analysis


```{r}
valueBox(paste("Manufacture vs Location"),color = "warning")

```

### Maximum Mileage in meters
```{r}
valueBox(max(data$Mileage),
         icon = "fa-car")
```

### State with Maximum production

```{r}
Location_count<-table(data$Location)
max_Location<-names(Location_count)[which.max(Location_count)]

valueBox(max_Location,
         icon = 'fa-car')
```


### **Average Mileage in meters**
```{r}
gauge(round(mean(data$Mileage),
            digits = 2),
            min = 0,
            max = 100000,
            gaugeSectors(success = c(60001, 100000),
                         warning = c(40001, 60000),
                         danger = c(0, 40000),
                         colors = c("green", "yellow", "red")))
```

Row
--------------------------------------------------

### New York

```{r}
valueBox(sum(data$Location == "New York"),
         icon = 'fa-car')
```

### Los Angeles

```{r}
valueBox(sum(data$Location == "Los Angeles"),
         icon = 'fa-car')
```

### Chicago

```{r}
valueBox(sum(data$Location == "Chicago"),
         icon = 'fa-car')
```

### Miami

```{r}
valueBox(sum(data$Location == "Miami"),
         icon = 'fa-car')
```

### Dallas

```{r}
valueBox(sum(data$Location == "Dallas"),
         icon = 'fa-car')
```


### Atlanta

```{r}
valueBox(sum(data$Location == "Atlanta"),
         icon = 'fa-car')
```

### Phoenix

```{r}
valueBox(sum(data$Location == "Phoenix"),
         icon = 'fa-car')
```

### Houston

```{r}
valueBox(sum(data$Location == "Houston"),
         icon = 'fa-car')
```

### Seattle

```{r}
valueBox(sum(data$Location == "Seattle"),
         icon = 'fa-car')
```

Row
-------------------------------

### Production By Model

```{r}
p1 <- data %>%
         group_by(Model) %>%
         summarise(count = n()) %>%
         plot_ly(x = ~Model,
                 y = ~count,
                 color = "blue",
                 type = 'bar') %>%
layout(xaxis = list(title = "Production By Model"),
yaxis = list(title = 'Count'))
p1
```


### Top States

```{r}
p2 <- data %>%
         group_by(Location) %>%
         summarise(count = n()) %>%
         filter(count>50) %>%
         plot_ly(labels = ~Location,
                 values = ~count,
                 marker = list(colors = mycolors)) %>%
         add_pie(hole = 0.2) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
p2
```


### Price Vs Mileage

```{r}
p3 <- plot_ly(data,
              x = ~Price,
              y = ~Mileage,
              text = paste("Price:", data$Price,
                           "Mileage:",
                           data$Mileage),
              type = "bar") %>%
         layout(xaxis = list(title="Price"),
                yaxis = list(title = "Mileage"))
p3
```


Row
------------------------------------
### Scatter Plot of Price Vs Mileage

```{r}
p4 <- plot_ly(data, x=~Price) %>%
         add_markers(y = ~Mileage,
                     text = ~paste("Mileage: ", Mileage),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(Mileage ~ Price)),
                   name = "Loess Smoother",
                   color = I("#FFC125"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Price"),
                yaxis = list(title = "Mileage"))
p4
```

### Box Plot of Top State

```{r}
data %>%
         group_by(Location) %>%
         ggvis(~Location, ~Mileage, fill = ~Location) %>%
         layer_boxplots()
```


Map
========================================

### Map

```{r}
car <- data %>%
         group_by(Location) %>%
         summarize(total = n())
car$Location <- abbr2state(car$Location)

highchart() %>%
         hc_title(text = "Car Production in US") %>%
         hc_subtitle(text = "Source: Car Data.csv") %>%
         hc_add_series_map(usgeojson, car,
                           name = "Location",
                           value = "total",
                           joinBy = c("Price", "Location")) %>%
         hc_mapNavigation(enabled = T)
```


Data Table
========================================

```{r}
datatable(data,
          caption = "Car Production",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))
```



Pivot Table
=========================================

```{r}
rpivotTable(data,
            aggregatorName = "Count",
            cols= "Price",
            rows = "Mileage",
            rendererName = "Heatmap")
```


Summary {data-orientation=columns}
===========================================

Column
-----------------------------------

### Max  Car Price

```{r}
valueBox(max(data$Price),
         icon = "fa-car" )
```

### Average Car Price
```{r}
valueBox(round(mean(data$Price),
               digits = 2),
         icon = "fa-area-chart")
```

### Average Mileage

```{r}
valueBox(round(mean(data$Mileage), digits = 2),
         icon = "fa-area-chart")
```




Column
---------------------------

Report

* This is a report on `r length(data$Car.ID)` car Production.

* The average Mileage of car was `r mean(data$Mileage)`.

* The average cost was `r mean(data$Price)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
========================================

Created by: Madhav Kumar at Lovely Professional University, Punjab

Confidential: HIGHLY!








