---
title: "MadhavKr12213356"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: ["twitter","instagram","facebook","menu"]
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
library(GGally)

```

RBI DATA
=======================================================================
```{r}

df<-read.csv("RBI DATA states_wise_population_Income.csv")

```

```{r}

mycolors <- c("#00ffff", "#c41e3a", "#fbceb1", "#ff4f00")

```


Row
-----------------------------------------------------------------------

### State wise population Income

```{r}

valueBox(paste("RBI DATA STATE WISE"),color = "skyblue")

```

### Maximum income of state for the year 2011

```{r}

max_income<-which(df$X2011.12.INC == max(df$X2011.12.INC))

valueBox(df$States_Union.Territories[max_income],color = "lightpink",icon = 'fa-building')

```


### **Average Literacy rate of India for the year 2011**

```{r}

gauge(round(mean(df$X2011..LIT),digits = 2),min = 0,max = 100,gaugeSectors(success = c(66,100),warning = c(34,66),danger = c(0,33),colors = c("green","pink","orange")))

```

Row
--------------------------------------------------------------------------

### Female per thousand Male in Bihar for the year 2011

```{r}

valueBox(df$X2011..SEX_Ratio[df$States_Union.Territories == "Bihar"],color = "#00ffff",icon = 'fa-female')

```

### Literacy rate in Bihar for the year 2011

```{r}

valueBox(df$X2011..LIT[df$States_Union.Territories == "Bihar"],color = "#7fffd4",icon = 'fa-user')

```

### Population of Bihar for the year 2011

```{r}

valueBox(df$X2011..POP[df$States_Union.Territories == "Bihar"],color = "#08e8de",icon = 'fa-female')

```

### Unemployment rate in Bihar for the year 2011

```{r}

valueBox(df$X2011..UNEMP[df$States_Union.Territories == "Bihar"],color = "#faf0be",icon = 'fa-user')

```

### Income of Bihar for the year 2011

```{r}

valueBox(df$X2011.12.INC[df$States_Union.Territories == "Bihar"],color = "#fffdd0",icon = 'fa-rupee')

```


Row
----------------------------------------------------------------------------

### States having **unemployment** rate greater then 30

```{r}

p1 <- df %>% filter(X2011..UNEMP > 30) %>% 
        
        plot_ly(labels = ~States_Union.Territories,
                values = ~X2011..UNEMP,
                marker = list(colors = mycolors)) %>%
        add_pie(hole = 0) %>%
        layout(xaxis = list(showline = F,
                            showgrid = F,
                            zeroline = F,
                            showticklabels = F),
               yaxis = list(showline = F,
                            showgrid = F,
                            zeroline = F,
                            showticklabels = F))
p1

```




### States having Poverty greater than 30 for the year 2011

```{r}

p2 <- df %>%
         filter(X2011..Poverty > 30) %>% 
         plot_ly(x = ~States_Union.Territories,
                 y = ~X2011..Poverty,
                 type = 'bar',
                 marker = list(color = 'green')) %>%
layout(xaxis = list(title = "State"),
yaxis = list(title = 'Poverty for the year 2011'))

p2

```


### Density plot of literacy rate in 2011


```{r}

density_plot <- plot_ly(df, x = ~`X2011..LIT`, type = "histogram", histnorm = "probability density",
                        marker = list(color = "blue"), opacity = 0.7, line = list(color = "black")) %>%
  layout(title = "Density Plot of Literacy Rate in 2011", xaxis = list(title = "Literacy Rate"))
density_plot


```



Charts
=================================

Column
------------------------------------

### Scatter Plot of 2011 Unemployment Vs 2011 Poverty

```{r}

plot_ly(data = df, x = ~`X2011..UNEMP`, y = ~`X2011..Poverty`,text = ~States_Union.Territories, type = "scatter", mode = "markers", marker = list(color = "red")) %>%
  layout(title = "2011 Unemployment vs. 2011 Poverty",
         xaxis = list(title = "2011 Unemployment"),
         yaxis = list(title = "2011 Poverty"))




```


### Box plot of literacy rate in 2001 and 2011

```{r}




boxplot <- plot_ly(df, y = ~`X2001...LIT`, type = "box", name = "2001") %>%
  add_trace(y = ~`X2011..LIT`, name = "2011") %>%
  layout(title = "Literacy Rate Comparison (2001 vs 2011)", yaxis = list(title = "Literacy Rate"))

boxplot



```


### Histogram of population in 2011

```{r}

histogram <- plot_ly(df, x = ~`X2011..POP`, type = "histogram", marker = list(color = "lightblue"), 
                     opacity = 0.7, line = list(color = "black")) %>%
  layout(title = "Population Distribution in 2011", xaxis = list(title = "Population"))
histogram



```



Column
--------------------------------------------------------------------

### Bubble chart of Population in 2001 vs Population in 2011


```{r}



bubble_chart <- plot_ly(df, x = ~X2001...POP, y = ~X2011..POP, size = ~X2011..LIT,
                        color = ~X2011..UNEMP, colors = "Blues", type = "scatter", mode = "markers",
                        text = ~paste("State/UT: ", States_Union.Territories,
                                      "<br>Population (2001): ", X2001...POP,
                                      "<br>Population (2011): ", X2011..POP,
                                      "<br>Literacy Rate (2011): ", X2011..LIT,
                                      "<br>Unemployment Rate (2011): ", X2011..UNEMP)) %>%
  layout(title = "Population Comparison (2001 vs 2011)",
         xaxis = list(title = "Population in 2001"),
         yaxis = list(title = "Population in 2011"))

bubble_chart

```


### Pie chart of unemployment rate in 2001

```{r}

unemployment_pie <- data.frame(Unemployment_Rate = c(sum(df$`X2001..UNEMP`), sum(df$`X2011..UNEMP`)),
                               Year = c("2001", "2011"))

pie_chart <- plot_ly(unemployment_pie, labels = ~Year, values = ~Unemployment_Rate, type = "pie",
                     textposition = "inside", hole = 0.4) %>%
  layout(title = "Unemployment Rate Comparison (2001 vs 2011)")
pie_chart

```


### Scatter plot matrix

```{r}


scatter_data <- df[, c("X2001...LIT", "X2011..LIT", "X2001...POP", "X2011..POP", "X2001..UNEMP", "X2011..UNEMP")]

scatter_matrix <- plot_ly(scatter_data, type = "scatter", mode = "markers", 
                          marker = list(size = 10, opacity = 0.5),
                          diagonal = list(visible = FALSE)) %>%
  add_trace(x = ~X2001...LIT, y = ~X2001...POP, name = "2001", type = "scatter", mode = "markers", 
            marker = list(color = "blue")) %>%
  add_trace(x = ~X2011..LIT, y = ~X2011..POP, name = "2011", type = "scatter", mode = "markers", 
            marker = list(color = "red")) %>%
  layout(title = "Literacy Rate vs Population",
         xaxis = list(title = "Literacy Rate"),
         yaxis = list(title = "Population"))

scatter_matrix

```


Bar chart
=========================================================

### Bar chart representing income of each state for the year 2011-12

```{r}
plot_ly(data = df, x = ~States_Union.Territories, y = ~`X2011.12.INC`, type = "bar", marker = list(color = "skyblue")) %>%
  layout(title = "2011-12 Income by States/Union Territories", xaxis = list(title = "States/Union Territories"), yaxis = list(title = "Income"))

```



Data Table
========================================

```{r}

datatable(df,
          caption = "RBI DATA",
          rownames = T,
          filter = "top",
          options = list(pageLength = 25))

```


Pivot Table
=========================================

```{r}


filtered_df <- df[df$`X2011..LIT` > 70, ]


rpivotTable(filtered_df,
            aggregatorName = "Count",
            cols = "States_Union.Territories",
            rows = "States_Union.Territories",
            rendererName = "Heatmap",
            width = "50%",  
            height = "400px",  
            rowLimit = 20,   
            colLimit = 20)  



```



Summary {data-orientation=columns}
===========================================

Column
-----------------------------------

### Maximum income of state for the year 2000 - 01

```{r}

valueBox(max(df$X2000.01.INC),
         icon = "fa-rupee" )

```

### Average income of India for the year 2000 - 01
```{r}
valueBox(round(mean(df$X2000.01.INC),
               digits = 2),
         icon = "fa-rupee")
```

### Average literacy rate of India for the year 2011 - 12

```{r}
valueBox(round(mean(df$X2011..LIT), digits = 2),
         icon = "fa-book")
```




Column
---------------------------

Report

* This is a report on `r length(df$States_Union.Territories)` Indian State and Union Territories.

* The average unemployment rate of India for the year 2011 was `r mean(df$X2011..LIT)`.

* The average poverty in India for the year 2011 was `r mean(df$X2011..Poverty)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
========================================

Created by: Madhav Kumar at Lovely Professional University, Punjab

Confidential: HIGHLY!



